\documentclass[10pt,a4paper,final, twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{quoting} 
\usepackage[LGR,T1]{fontenc}
\newcommand{\textgreek}[1]{\begingroup\fontencoding{LGR}\selectfont#1\endgroup}
\usepackage[a4paper,margin=0.5in]{geometry}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{hyperref}


\renewcommand{\thefootnote}{\Alph{footnote}}
\renewcommand{\textsuperscript}[1]{\ensuremath{^{\textbf{\scriptsize #1}}}}

\begin{document}

The NET’s uniquely transparent, accountable translation process has been crystalized in the most extensive set of Bible translators’ notes ever created. More than 60,000 notes highlight every major decision, outline alternative views, and explain difficult or nontraditional renderings. These are broken into: \textbf{sn} Study Notes, \textbf{tn} Translation Notes, and \textbf{tc} Text Critical notes (comparison of different manuscripts). Available at \url{https://www.netbible.org}

\section*{1 Tim 2-3 (NET)}




\subsection*{Prayer for All People}

\textsuperscript{1} First of all, then, I urge that requests, prayers, intercessions, and thanks be offered on behalf of all people, \textsuperscript{2} even for kings and all who are in authority, that we may lead a peaceful and quiet life in all godliness and dignity. \textsuperscript{3} Such prayer for all is good and welcomed before God our Savior, \textsuperscript{4} since he wants all people to be saved and to come to a knowledge of the truth. \textsuperscript{5} For there is one God and one intermediary between God and humanity, Christ Jesus, himself human, \textsuperscript{6} who gave himself as a ransom for all, revealing God’s purpose at his appointed time. \textsuperscript{7} For this I was appointed a preacher and apostle—I am telling the truth; I am not lying—and a teacher of the Gentiles in faith and truth. \textsuperscript{8} So I want the men\footnote{\textbf{tn} The word translated ``men'' refers to adult males, not people in general. Note the command given to ``the women'' in v9} to pray in every place, lifting up holy hands without anger or dispute\footnote{\textbf{sn} Paul uses a common ancient posture in prayer (lifting up holy hands) as a figure of speech for offering requests from a holy life (without anger or dispute)}. 


\subsection*{Conduct of Women}

\textsuperscript{9} Likewise the women are to dress in suitable apparel, with modesty and self-control. Their adornment must not be with braided hair and gold or pearls or expensive clothing, \textsuperscript{10} but with good deeds, as is proper for women who profess reverence for God. \textsuperscript{11} A woman must learn quietly with all submissiveness. \textsuperscript{12} But I do not allow a woman to teach or exercise authority\footnote{\textbf{tn} According to BDAG 150 s.v. authenteo this Greek verb means “to assume a stance of independent authority, give orders to, dictate to” (cf. Jerusalem Bible ``tell a man what to do”)} over a man. She must remain quiet. \textsuperscript{13} For Adam was formed first and then Eve. \textsuperscript{14} And Adam was not deceived, but the woman, because she was fully deceived, fell into transgression. \textsuperscript{15} But she will be delivered through childbearing, if she continues in faith and love and holiness with self-control. 


\subsection*{Qualifications for Overseers and Deacons}

\textsuperscript{3:1} This saying is trustworthy: “If someone aspires to the office of overseer, he desires a good work.” \textsuperscript{2} The overseer then must be above reproach, the husband of one wife, temperate, self-controlled, respectable, hospitable, an able teacher, \textsuperscript{3} not a drunkard, not violent, but gentle, not contentious, free from the love of money. \textsuperscript{4} He must manage his own household well and keep his children in control without losing his dignity. \textsuperscript{5} But if someone does not know how to manage his own household, how will he care for the church of God? \textsuperscript{6} He must not be a recent convert or he may become arrogant and fall into the punishment that the devil will exact. \textsuperscript{7} And he must be well thought of by those outside the faith, so that he may not fall into disgrace and be caught by the devil’s trap. 
\textsuperscript{8} Deacons likewise must be dignified, not two-faced, not given to excessive drinking, not greedy for gain, \textsuperscript{9} holding to the mystery of the faith with a clear conscience. 3:10 And these also must be tested first and then let them serve as deacons if they are found blameless. \textsuperscript{11} Likewise also their wives must be dignified, not slanderous, temperate, faithful in every respect. \textsuperscript{12} Deacons must be husbands of one wife and good managers of their children and their own households. \textsuperscript{13} For those who have served well as deacons gain a good standing for themselves and great boldness in the faith that is in Christ Jesus. 


\subsection*{Conduct in God’s Church}

\textsuperscript{14} I hope to come to you soon, but I am writing these instructions to you \textsuperscript{15} in case I am delayed, to let you know how people ought to conduct themselves in the household of God, because it is the church of the living God, the support and bulwark of the truth. \textsuperscript{16} And we all agree, our religion contains amazing revelation: \\
    He was revealed in the flesh, \\
    vindicated by the Spirit, \\
    seen by angels, \\
    proclaimed among Gentiles, \\
    believed on in the world, \\
    taken up in glory. 

\subsubsection*{AI summary of the church in Ephesus}
False teaching was widespread throughout the church community, including incorrect instructions about the law and ancestry, commands to abstain from marriage and certain foods, and a focus on myths and false `knowledge'\textsuperscript{1,2}. These false teachers had particularly influenced many of the women in the congregation, with some women being described as ``weak women burdened with sins and led astray by various passions, always learning and never able to arrive at knowledge of the truth''\textsuperscript{3}. The problems extended to behavioral issues, including anger and quarrelling among the men\textsuperscript{1,4}, and immodest or ostentatious dress among the women\textsuperscript{1}. Additionally, women were overstepping boundaries by desiring to be teachers of the law and rulers within the church\textsuperscript{4}, and there were issues with church widows who had pledged singleness but chose to remarry, threatening the church's credibility\textsuperscript{4}. The cultural context reveals that from about 44 BC onward, women in some circles of the Roman Empire had claimed bold new freedom, with the emergence of a "new woman" that concerned philosophers and rulers who worried about family morality breakdown\textsuperscript{2}. The uneducated women in Ephesus seemed to provide the network that false teachers used to spread their teachings through the congregations, likely because they were not as well learned in the Scriptures as men\textsuperscript{5}.\\
\textsuperscript{1}Adams, Katia. Equal: What the Bible Says about Women, Men, and Authority. David C Cook, 2019.
\textsuperscript{2}Zehr, Paul M. 1 \& 2 Timothy, Titus. Herald Press, 2010, p. 61.
\textsuperscript{3}Severance, Diana Lynn. Feminine Threads. Christian Focus, 2012.
\textsuperscript{4}Farley, Lawrence R. Shepherding the Flock: The Pastoral Epistles of St. Paul the Apostle to Timothy and to Titus. Ancient Faith Publishing, 2007, p. 16.
\textsuperscript{5}Keener, Craig S. Paul, Women \& Wives: Marriage and Women’s Ministry in the Letters of Paul. Hendrickson Publishers, 1992, p. 111.


\end{document}
